---
author: "Emi"
output: 
  html_document:
    code_folding: hide
    number_sections: true
---
# Sample specs

```{r sample_specs}
# RUN THIS BEFORE KNITTING!!!
specs <- list('idSample' = 'p_A99_b97q4_fh03q4',
      'savingFolder' = 'output/probit/Annual99/',
      'y' = list('failureSince' = 2000.1,
                 'failureHorizon' = 2003.4),
      'X' = list('freq' = 'annual',
                 'from' = 1999,
                 'to' = 1999,
                 'bankBirthFrom' = 1997.4, 
                 'vars' = c('ActivoN', 'C8Est_w', 'CAR_IRR_3A6', 'P_ROA',
                            'P_DEP_ARS_RATE',
                            'P_LOANS_ARS_RATE_W', 'APRSpNF_RATE_W', 'APR_USD_RATE',
                            'APR_RATE_W')),
      'W' = list('from' = NULL,
                 'to' = NULL,
                 #Weights from debtor/creditor perspective : W_D_PR/W_A_PR (Deudora / Acreeedora)
                 'wVar' = NULL))
```

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
library(tidyverse)
library(lubridate)
library(tsibble) # Panel data/longitudinal
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(writexl)
library(svglite) # export plots to svg
library(rmatio) # expor to Matlab
library(spdep)
library(spatialreg)
source('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/code/Rutils/Emi_R_utils.R')

```

```{=html}
<style type="text/css">
  .main-container {
    max-width: 1100px;
    margin-left: auto;
    margin-right: auto;
  }
</style>
```

---
  title: `r specs$idSample`
  date: `r today()`
---
  
-   Only banks that were alive by ```r specs$X$bankBirthFrom```

-   $\bm{y_t}$ is 1 if the bank fails between ```r specs$y$failureSince``` and ```r specs$y$failureHorizon```.

-   $X$ is data from `r specs$X$from` to `r specs$X$to`.

# Load data

## Banks covariates
```{r load_bank_data}
banksDB <- haven::read_dta('data/failures-1997-2001-annual.dta') %>%
  dplyr::mutate(., 
                fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
                exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
                startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
                .after = IDENT) 

banks <- banksDB %>%
  drop_na %>%
  filter(FECHA_A == specs$X$from) %>%
  # ONly private banks
  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5) %>%
  filter(startDateQ<= !!specs$X$bankBirthFrom & exitDateQ >= !!specs$y$failureSince) 

```

```{r}
setwd('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
#banksDB <- haven::read_dta('data/BAFA-main-1997-2001-quarterly.dta') %>%
#        dplyr::mutate(., 
#        fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
#        exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
#        startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
#        .after = IDENT) %>%
#    drop_na %>%
#  # For fix W I need to fix banks at the beginning of the sample
#  filter(startDateQ<= 1997.4 & exitDateQ>=2000.1) %>%
#  # ONly private banks
#  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5)

# Select only entities private and alive on 1997q4
banksAtStart <- banksDB %>%
  dplyr::group_by(IDENT) %>%
  summarise('start' = FECHA_A,
            'startDateQ' = min(startDateQ),
            NOMRED = first(NOMRED),
            GRUPO_ID_UNI = first(GRUPO_ID_UNI),
            P_LOANS_ARS_RATE_W = first(P_LOANS_ARS_RATE_W))

excBanks <- filter(banksDB, startDateQ>1997.4)
```

I lose ```r NROW(excBanks)``` banks because a) they don't have complete observations by 1997.4 (missing P_LOANS_ARS_RATE) or b) they were privatised after 1997q4.

```{r}
excBanks
```

Hence I end up with ```r banks$IDENT %>% unique() %>% NROW()``` banks and the mean of IDENT is ```r banks$IDENT %>% mean()```.


# Estimation of a probit model

## Build objects

```{r}
X <- banks %>% select(all_of(specs$X$vars))

# 1: survival, 0: failure during the sample period
y <- if_else(banks$exitDateQ <= specs$y$failureHorizon, 0, 1)

```

```{r sample_save}
saveRDS(bind_cols('DEP_VAR' = y, X), file=paste0(specs$savingFolder, specs$idSample, '_sample.rds'))
#write.mat(list('Wstd' = Wstd,
#               'X' =  X %>% data.matrix(.),
#               'y' = y),
#          'data.mat')
```

## Desc stats

```{r descStatsBanks}
dplyr::bind_cols('y'=y, X, 'IDENT'=banks$IDENT) %>%
  descStats2(.)
```

## Run!
```{r estimation_sar}
model <- glm(formula ='y ~ ActivoN + C8Est_w + CAR_IRR_3A6+ P_ROA+ P_DEP_ARS_RATE +
        P_LOANS_ARS_RATE_W+ APRSpNF_RATE_W+ APR_USD_RATE+ APR_RATE_W',
        data = bind_cols('y'=y, X),
    family=binomial(link='probit'), 
    x=TRUE)

regSumm <- summary.glm(model)

regSumm
```

## Compute marginal effects

A $1- \alpha$ confidence interval for $\hat{\beta_k}$ is $\hat{\beta_k} \pm z_{\frac{\alpha}{2}} \: \frac{\hat{\sigma_k}}{\sqrt{n}}$

```{r marginalEffects}
# Compute marginal effects
# Marginal probabilities
pMarginals <- dnorm( model$x %*% model$coefficients )

# Marginal effect of the average bank
x_Bar <- apply(model$x, MARGIN=2, mean) # Kx1 vector
pMarginalAvgBank <- dnorm( t(x_Bar) %*% reg$coefficients)

mgEffects <- pmap_dfr(as_tibble( regSumm$coefficients, rownames='var'), 
         function(var, Estimate, `Std. Error`, ...) { 
# CAMERON TRIVEDIR p467. Avergae Marginal effect of variable j is the average (over observations) of pdf(X Beta) * \hat{\beta}_j
  n = NROW(regSumm$deviance.resid)
  tibble('var' = var, 
         'AVG_EFFECT_MEAN' = mean(pMarginals * Estimate),
         'AVG_EFFECT_MIN_90' = AVG_EFFECT_MEAN - 1.645 * (`Std. Error`)*(1/sqrt( n )), 
         'AVG_EFFECT_MAX_90' = AVG_EFFECT_MEAN + 1.645 * (`Std. Error`)*(1/sqrt( n )))
}) 

mgEffects
  
  
```

## Save results
```{r }
saveRDS(model, file=paste0(specs$savingFolder, specs$idSample, '_reg.rds'))

#outList <- list(NULL)
#names(outList) <- specs$idSample
estimatesTibble <- as_tibble(regSumm$coefficients) %>%
  rename('EST_COEF' = 'Estimate',
         'STD_ERROR' ='Std. Error',
         'Z_VALUE' ='z value',
         'P_VALUE' = 'Pr(>|z|)') %>%
  mutate('ID_SAMPLE' = specs$idSample,
    'PREDICTOR' = rownames(regSumm$coefficients), .before=1) %>%
  bind_cols(., select(mgEffects, 
            AVG_EFFECT_MEAN, AVG_EFFECT_MIN_90, AVG_EFFECT_MAX_90)) %>%
  mutate('MODEL_AIC' = regSumm$aic,
         'MODEL_N' = NROW(regSumm$deviance.resid))

write_excel_csv(estimatesTibble, file = paste0('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/output/probit/results_probit.csv'),
                append=TRUE)
```