---
title: "Graph 1997m6-2001m12"
author: "Emi"
date: "10/02/2021"
output: html_document
   #code_folding: hide
---
<style type="text/css">
.main-container {
  max-width: 1000px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure')
library(tidyverse)
library(lubridate)
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(xlsx)
library(svglite) # export plots to svg
#source('FunsMisc.R')
```

# INtroduction
I build the network monthly. 
Then I take quarterly averages of the matrix W obtaining quarterly networks.
Then I filter W to include only the banks that are considered in the quarterly probit model. 

## Loading data

Load the database from Stata:

```{r load_and_filter}

dbRelations <- read_dta('data/interLoans/cen_deu_annual.dta')
```

```{r network_by_date}
#relations <- filter(relations, !is.na(IDent))
#atDate <- ymd("1998-03-01")
atDate <- 1998
sam <- readRDS('code/probit/failureTill2001q4/annual/sam_s98.Priv.01.onT.rds')

theseRelations <- dbRelations %>% 
                  #dplyr::filter(., W_A_PR>0.0001) %>%
                  dplyr::filter(., FECHA_A == atDate) %>%
                  filter(., IDENT_ACREEDORA != IDENT_DEUDORA) %>%
                  select(IDENT_ACREEDORA, IDENT_DEUDORA, W_A_PR) %>%
                  rename(WEIGHT = W_A_PR) %>%
                  mutate(WEIGHT = WEIGHT*100)
# W can only contains entities that are in the sample. 
theseRelations <- semi_join(theseRelations, select(sam, IDENT), by= c('IDENT_ACREEDORA' = 'IDENT')) %>%
                  semi_join(., select(sam, IDENT), by= c('IDENT_DEUDORA' = 'IDENT'))
  

# Nodes
#

#grupoStr <- tibble('grupoIDUni' = c(1:9, NA),
#                    'type' = c('Local corporation', 'Cooperative', 'Local corporation', 'State-owned', 'State-owned', 'Foreign branch', 'Caja', 'Non-bank', 'Non-bank', 'Non-bank'))


#nodes <- filter(dbFcialEnts, FECHAdata==atDate) %>%
#          dplyr::select(., !FECHAdata) %>%
          #left_join(., grupoStr, by='grupoIDUni')
#
nodes <- select(sam, IDENT, NOMRED, EXIT_DATE_Q:GRUPO_ID_UNI)
g <- graph_from_data_frame(d = theseRelations, 
                           vertices = nodes,
                          directed = TRUE)

# Export adjacency matrix
W_weighted <- as_adjacency_matrix(g, attr='WEIGHT', sparse=FALSE)
W <- as_adjacency_matrix(g, attr=NULL, sparse=FALSE)
sumCols <- apply(W, MARGIN=2, sum)
write.table(W_weighted, file='code/standardSpatialProbit/W_weighted_1998.csv', 
            sep=', ',
            row.names = F, col.names = F)

write.table(W, file='code/standardSpatialProbit/annualW_1998.csv', 
            sep=', ',
            row.names = F, col.names = F)

# Export covariates


```

Sparsity of W is ```{r} (sum(sumCols)/(NCOL(W)*NROW(W)))*100 ``` %


## Relations: distribution of weights

```{r weight_density}
#thisRelations <- dplyr::filter(theseRelations, FECHAdata == atDate)
#group_by(theseRelations, FECHAdata) %>%
  descStatsW <- summarise(theseRelations,
          'Links' = n(),
          'N_CREDITORS' = n_distinct(IDENT_ACREEDORA),
          'N_DEBTORS' = n_distinct(IDENT_DEUDORA),
          'MEAN_WEIGHT_PC' = round(mean(WEIGHT), 2),
          'Median weight' = round(median(WEIGHT)),
          'CV weight' =  round((MEAN_WEIGHT_PC) / sd(WEIGHT), 2),
          '1st quartile_PC' = round(quantile(WEIGHT, probs=.25), 2))
          
descStatsW

linksPerBank <- theseRelations %>%
group_by(IDENT_ACREEDORA) %>%
summarise('Links' = n())

linksPerBank

```

#ggplot(data=thisRelations[, 'WEIGHT'], mapping=aes(x=WEIGHT)) +
#  scale_x_continuous(breaks=seq(0, 0.35, by=0.05)) +
#  geom_dotplot()
#
#ggplot(data=thisRelations[, 'WEIGHT'], mapping=aes(x=WEIGHT)) +
#  scale_x_continuous(breaks=seq(0, 0.35, by=0.05)) +
#  geom_boxplot()

Acces a specific node (vertix):

```{r}
V(g)[[1]]
```

gives all the details about the first vertix.

We can plot g

```{r plot}
library(ggraph) 
ggraph(g, layout='fr', weights=WEIGHT ) +
  geom_edge_link() +
  geom_node_point(aes(size = centrality_pagerank())) +
  theme(legend.position = 'bottom')

Pstatic <- ggraph(g, layout='fr', weights=WEIGHT ) +
            # geom_edge_fan(aes(width=WEIGHT, colour=stat(index)),
            geom_edge_fan(aes(alpha=WEIGHT),
                          arrow = arrow(length=unit(1, 'mm')), end_cap = circle(2, 'mm')) +
            geom_node_point(aes(size = (Activo/1000000), colour=factor(type)), alpha=.8) +
            #geom_node_text(aes(label = bNombre), repel=TRUE, check_overlap = TRUE) + 
  scale_size(breaks=c(1, 5, 10, 15), labels=c('<=1', '5', '10', '15'))          +
  theme(legend.position = 'bottom') +
            guides(size=guide_legend(title='Assets (billions pesos)', title.position='top', nrow=3, ncol=2, byrow=TRUE),
                   colour=guide_legend(title='Organizational type', title.position='top', override.aes=list(size=5), nrow=3, byrow=TRUE),
                   edge_alpha=guide_legend(title='Share from lender bank', title.position='top', nrow=3, byrow=TRUE))

#Pstatic
#ggsave('Pstatic.pdf', plot=Pstatic)
#ggsave('Pstatic.svg', plot=Pstatic)

```

## Interactive plot

Using visNetwork package. I use the same 'g' object from iGraph

```{r plot_interactive, eval=TRUE}
pTblNodes <- nodes %>%
  dplyr::select(., IDENT, NOMRED, ActivoN) %>%
  dplyr::transmute(., id=IDENT, label=NOMRED, value=ActivoN, title=str_c(NOMRED, ', $ ', round((ActivoN/1000000), digits=2), ' bill.'))

pTblRelations <- theseRelations %>%
  dplyr::transmute(., from=IDENT_ACREEDORA, to=IDENT_DEUDORA, value=WEIGHT, arrows='to')

visNetwork(nodes = pTblNodes, edges = pTblRelations, height = "900px", width = "100%")  %>% 
  visNodes(mass=15, scaling=list('min'=5,'max'=20)) %>%
  visEdges(scaling=list('min'=1, 'max'=5)) %>%
  visLayout(randomSeed=123, improvedLayout=TRUE) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE, collapse=TRUE) %>%
  visInteraction(navigationButtons = TRUE) %>%
  visPhysics(enabled = FALSE, maxVelocity = 0.75)

#   %>%
#  visConfigure(enabled = TRUE)
#%>%
#  visNodes(scaling=list())



#visIgraph(g) %>%
#  visNodes(shape='square', size = WEIGHT)
```

