---
title: "Estimation and inference in probit model"
author: "Emi"
date: "28/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
```

## R Markdown

Load 3 samples of different sizes. They were simulated by the Matlab script.
```{r load_simulated_data}
sams <- list('n36' = list('X' = read_csv('../../probit/Xsim-36.csv', col_names=FALSE),
                          'Y' = read_csv('../../probit/Ysim-36.csv', col_names=FALSE)),
                'n100' = list('X' = read_csv('../../probit/Xsim-100.csv', col_names=FALSE),
                              'Y' = read_csv('../../probit/Ysim-100.csv', col_names=FALSE)),
                'n500' = list('X' = read_csv('../../probit/Xsim-500.csv', col_names=FALSE),
                              'Y' = read_csv('../../probit/Ysim-500.csv', col_names=FALSE)))
                
```

## Estimation & inference

### Correct estimation
Compute estimation using Generalised Least Sqaures with error term following a Biomial (Bernoulli)

```{r estimation, echo=FALSE}
results <- map_dfc(sams, function(sample)
  {
  Y <- as.matrix(sample$Y)
  X <- as.matrix(sample$X)
  
  p <- glm(Y ~ X, family=binomial(link='probit'))
  summary.glm(p) %$%
    c(.$coefficients[,1], .$coefficients[,3])

  })
results
```

means
results[[3]]$coefficients[,1]

z-values
results[[1]]$coefficients[,3]

The first 4 rows correspond to mean coefficients and the last 4 rows correspond to the Z-value. See the comparison in the file C:\\Users\\emi.ABLE-22868\\OneDrive\\UWA PhD\\bankFailure\\code\\probit\\Probit simulation results.xlsx
