---
author: "Emi"
output: 
  html_document:
    code_folding: hide
    number_sections: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
library(tidyverse)
library(lubridate)
library(tsibble) # Panel data/longitudinal
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(writexl)
library(svglite) # export plots to svg
library(rmatio) # expor to Matlab
library(spdep)
library(spatialreg)
library(huxtable) # export tables (tibble) to Latex/Excel
source('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/code/Rutils/Emi_R_utils.R')

```

```{=html}
<style type="text/css">
  .main-container {
    max-width: 1100px;
    margin-left: auto;
    margin-right: auto;
  }
</style>
```

# Sample specs

```{r sample_specs}
# RUN THIS BEFORE KNITTING!!!
specs <- list('idSample' = 'A99_Wtill98q4_creW_b97q4_s03q4',
              'savingFolder' = 'output/SAR/Annual99/',
              'y' = list('failureSince' = 2000.1,
                         'failureHorizon' = 2003.4),
              'X' = list('freq' = 'annual',
                         'from' = 1999,
                         'to' = 1999,
                         'bankBirthFrom' = 1997.4, 
                         'vars' = c('ActivoN', 'C8Est_w', 'CAR_IRR_3A6', 'P_ROA',
  'P_DEP_ARS_RATE', 'P_LOANS_ARS_RATE_W', 'APRSpNF_RATE_W', 'APR_USD_RATE', 'APR_RATE_W')),
              'W' = list('from' = '',
                         'to' = '1998q4',
                         #Weights from debtor/creditor perspective : W_D_PR/W_A_PR (Deudora / Acreeedora)
                         'wVar' = 'W_A_PR'))
```

---
  title: `r specs$idSample`
  date: `r today()`
---
  
-   Only banks that were alive by ```r specs$X$bankBirthFrom```

-   $\bm{y_t}$ is 1 if the bank fails between ```r specs$y$failureSince``` and ```r specs$y$failureHorizon```.

-   $W$ is the average between the beginning of data (around 1997q3) and ```r specs$W$to```. Hence we use past information about the network.

-   $X$ is data from `r specs$X$from` to `r specs$X$to`.

# Load data

## Banks covariates
```{r load_bank_data}
banksDB <- haven::read_dta('data/failures-1997-2001-annual.dta') %>%
  dplyr::mutate(., 
                fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
                exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
                startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
                .after = IDENT) 

banks <- banksDB %>%
  drop_na %>%
  filter(FECHA_A == specs$X$from) %>%
  # ONly private banks
  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5) %>%
  filter(startDateQ<= !!specs$X$bankBirthFrom & exitDateQ >= !!specs$y$failureSince) 

```

```{r}
setwd('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
#banksDB <- haven::read_dta('data/BAFA-main-1997-2001-quarterly.dta') %>%
#        dplyr::mutate(., 
#        fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
#        exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
#        startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
#        .after = IDENT) %>%
#    drop_na %>%
#  # For fix W I need to fix banks at the beginning of the sample
#  filter(startDateQ<= 1997.4 & exitDateQ>=2000.1) %>%
#  # ONly private banks
#  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5)

# Select only entities private and alive on 1997q4
banksAtStart <- banksDB %>%
  dplyr::group_by(IDENT) %>%
  summarise('start' = FECHA_A,
            'startDateQ' = min(startDateQ),
            NOMRED = first(NOMRED),
            GRUPO_ID_UNI = first(GRUPO_ID_UNI),
            P_LOANS_ARS_RATE_W = first(P_LOANS_ARS_RATE_W))

excBanks <- filter(banksDB, startDateQ>1997.4)
```

I lose ```r NROW(excBanks)``` banks because a) they don't have complete observations by 1997.4 (missing P_LOANS_ARS_RATE) or b) they were privatised after 1997q4.

```{r}
excBanks
```

Hence I end up with ```r banks$IDENT %>% unique() %>% NROW()``` banks and the mean of IDENT is ```r banks$IDENT %>% mean()```.

## Network data

```{r load_network_data}
setwd('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
dbRelations <- read_dta('data/interLoans/cen_deu_1997-06_2001_quarterly.dta') %>%
  mutate(FECHA_Q = ( as_date(FECHA_D, origin=ymd("1960-01-01")) %>% 
                     tsibble::yearquarter(.) ),
         WEIGHT = .data[[ specs$W$wVar]]*100) %>%
  tsibble(key = c(IDENT_ACREEDORA, IDENT_DEUDORA), 
          index = FECHA_Q)

# W_A_PR W_D_PR
thisRelations <- filter_index(dbRelations, ~ specs$W$to) %>%
  # fechaQ >= 1997.4 &
  filter(., (IDENT_ACREEDORA != IDENT_DEUDORA) &
  WEIGHT != 0)

thisRelations

# Number of unique relations (links)
uLinksN <- select(thisRelations, IDENT_ACREEDORA, IDENT_DEUDORA) %>%
  distinct() %>%
  nrow()

uLinksN

```

# Estimation of a (linear) SAR model

## Build objects

### X and Y
```{r}
X <- banks %>% select(all_of(specs$X$vars))

# 1: survival, 0: failure during the sample period
y <- if_else(banks$exitDateQ <= specs$y$failureHorizon, 0, 1)

```

### Build the Average Network

$W$ is the average for each link between the beginning and ```r specs$W$to``` for all banks

```{r}
# Reconvert to tibble because tsibble cannot drop the groupping by time (index)
avgRelations <- thisRelations %>%
  as_tibble(.) %>%
  group_by(IDENT_ACREEDORA, IDENT_DEUDORA) %>%
  summarise(WEIGHT = mean(WEIGHT)) %>%
  # W can only contains entities that are in the sample. 
  semi_join(., select(banks, IDENT), 
    by= c('IDENT_ACREEDORA' = 'IDENT')) %>%
  semi_join(., select(banks, IDENT), 
    by= c('IDENT_DEUDORA' = 'IDENT')) 
  #filter(., WEIGHT<0.1)
# This dataframe should be empty
netExcBanks <- bind_rows(anti_join(avgRelations, banks, by=c('IDENT_ACREEDORA' = 'IDENT')),
                    anti_join(avgRelations, banks, by=c('IDENT_DEUDORA' = 'IDENT')))

avgRelations

#setwd(samPath)
#writexl::write_xlsx(avgRelations, path='avgRelations.xlsx')

```

The following entities appear in the network but not in the banks dataframe: NROWS: `r NROW(netExcBanks)`. Should be empty!

#### Export average network as spatial matrix

Create a network (igraph) object and the spatial matrix `W` which only contains banks that are in `banks`

```{r }
nodes <- banks %>%
  select(., IDENT, NOMRED, ActivoN) %>%
  mutate(survival = y)
  
network <- igraph::graph_from_data_frame(d = avgRelations, 
                           vertices = nodes,
                          directed = TRUE)

# Export adjacency matrix
W_weighted <- as_adjacency_matrix(network, attr='WEIGHT', sparse=FALSE)
W <- as_adjacency_matrix(network, attr=NULL, sparse=FALSE)
# Dimensions of W should equal # of banks
# Row-normalised weight matrix
Wstd <- apply(W_weighted, MARGIN=1, FUN=function(row) { 
  rowSum = sum(row)
  if (rowSum != 0) {
    row/rowSum
  } else {
    row
  }}) %>% t(.)

spatialRegNetwork <-  spdep::mat2listw(Wstd) 
```

There are ```r nrow(thisRelations)``` links in `avgRelations`; ```r uLinksN``` of them are unique. `W` is `r nrow(W)` $\times$ `r ncol(W)` and the number of banks in `banks` is `r NROW(banks)`. They should be equal!

## Desc stats

```{r descStatsBanks}
descStatsT <- dplyr::bind_cols('y'=y, X, 'IDENT'=banks$IDENT) %>%
  descStats2(.)

  descStatsT %>%
    datatable() %>%
    formatRound(columns=c('min', 'median', 'mean', 'SD', 'max', 'CV'))
```

```{r descStats_network}
summary(spatialRegNetwork, zero.policy=TRUE)
```

## Run!
```{r estimation_sar}
model <- spatialreg::lagsarlm(formula ='y ~ ActivoN+ C8Est_w+ CAR_IRR_3A6+ P_ROA+ P_DEP_ARS_RATE +
  P_LOANS_ARS_RATE_W+ APRSpNF_RATE_W+ APR_USD_RATE+ APR_RATE_W',
        data = bind_cols('y'=y, X),
        listw = spatialRegNetwork,
        zero.policy = TRUE)

regSumm <- summary(model)

regSumm

```

Impacts:

```{r}
spatialreg::impacts(model, listw=spatialRegNetwork) %>%
  print()
```

# Save

## Sample
```{r sample_save}
saveRDS(bind_cols('DEP_VAR' = y, X), 
        file=paste0(specs$savingFolder, specs$idSample, '_sample.rds'))

saveRDS(network, 
        file=paste0(specs$savingFolder, specs$idSample, '_network.rds'))
#write.mat(list('Wstd' = Wstd,
#               'X' =  X %>% data.matrix(.),
#               'y' = y),
#          'data.mat')
```

## Results
```{r }

as_hux(descStatsT) %>% quick_xlsx(paste0(specs$savingFolder, 'desc_stats_table.xlsx'))

saveRDS(model, file=paste0(specs$savingFolder, specs$idSample, '_model.rds'))

rhoZvalue <- (regSumm$rho / regSumm$rho.se) %>% abs()
rhoPvalue = (1-pnorm(rhoZvalue))*2

#outList <- list(NULL)
#names(outList) <- specs$idSample
estimatesTibble <- as_tibble(regSumm$Coef) %>%
  rename('EST_COEF' = 'Estimate',
         'STD_ERROR' ='Std. Error',
         'Z_VALUE' ='z value',
         'P_VALUE' = 'Pr(>|z|)') %>%
  mutate('ID_SAMPLE' = specs$idSample,
    'PREDICTOR' = rownames(regSumm$Coef), .before=1) %>%
  add_row(ID_SAMPLE = specs$idSample, PREDICTOR='rho', 
          EST_COEF = regSumm$rho, STD_ERROR = regSumm$rho.se,  Z_VALUE = rhoZvalue, 
          P_VALUE = rhoPvalue) %>%
  mutate('MODEL_LOG_LIK_LM' = regSumm$logLik_lm.model,
         'MODEL_N' = NROW(regSumm$fitted.values),
         'WALD_TEST_SDEPENDANCE_PVALUE' = regSumm$Wald1$p.value,
         'LR_TEST_SDEPENDANCE_PVALUE' = regSumm$LR1$p.value)

write_excel_csv(estimatesTibble, file = paste0('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/output/results_main.csv'),
                append=TRUE)
```