---
  title: "PanelSAR_FixW_9704"
author: "Emi"
date: "10/02/2021"
output: html_document
#code_folding: hide
---

```{=html}
<style type="text/css">
  .main-container {
    max-width: 1000px;
    margin-left: auto;
    margin-right: auto;
  }
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
library(tidyverse)
library(lubridate)
library(tsibble) # Panel data/longitudinal
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(writexl)
library(svglite) # export plots to svg
source('../../../code/Rutils/Emi_R_utils.R')

samPath = 'data/SAMPLES/PanelSAR_FixW_9704/'
```

# INtroduction

$\bm{y_t}$ is the indicator vector for quarter $t$ such that if bank $i$ fails by quarter $i$, $y_{i, t} = 1$.\

\item

$W$ is the average between 1997q4 and 2000q3

\item

For each quarter $t$, $X_t$ is the average of $X$ the previous 4-quarters.

# Load data

```{r load_bank_data}
banksDB <- haven::read_dta('data/BAFA-main-1997-2001-quarterly.dta') %>%
        dplyr::mutate(., 
        fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
        exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
        startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
        .after = IDENT) %>%
    drop_na %>%
  # For fix W I need to fix banks at the beginning of the sample
  filter(startDateQ<= 1997.4) %>%
  # ONly private banks
  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5)

# Select only entities private and alive on 1997q4
banksAtStart <- banksDB %>%
dplyr::group_by(IDENT) %>%
  summarise('start' = min(fechaQ),
            'startDateQ' = min(startDateQ),
            NOMRED = first(NOMRED),
            GRUPO_ID_UNI = first(GRUPO_ID_UNI),
            P_LOANS_ARS_RATE_W = first(P_LOANS_ARS_RATE_W))

excBanks <- filter(banksAtStart, start>1997.4)
```
I lose the following 13 banks because a) they don't have complete observations by 1997.4 (missing P_LOANS_ARS_RATE) or b) they were privatised after 1997q4.

```{r}
excBanks
```

Hence the banks are:
```{r}
# All rows in banks that do not have a matrhc in excBanks
banks <- anti_join(banksDB, excBanks, by='IDENT') %>%
  mutate(fechaQ2 = yearquarter(fechaQ))
  )
  as_tsibble(., key = IDENT, index = fechaQ)

banks %>%
  scan_gaps()
banks %>%
  group_by_key() %>%
  fill_gaps() %>%
  tidyr::fill(P_ROA, .direction = "down")
banks
```

```{r load_network_data}
dbRelations <- read_dta('data/interLoans/cen_deu_1997-06_2001_quarterly.dta') %>%
  mutate(fechaQ = quarter(as_date(FECHA_D, origin=ymd("1960-01-01")), with_year=TRUE))

thisRelations <- filter(dbRelations, 
      # fechaQ >= 1997.4 &
  fechaQ <= 2000.4 &
  (IDENT_ACREEDORA != IDENT_DEUDORA) &
  W_A_PR != 0) %>% 
  rename(WEIGHT = W_A_PR) %>% mutate(WEIGHT = WEIGHT*100)

thisRelations

# Number of unique relations (links)
uLinksN <- select(thisRelations, IDENT_ACREEDORA, IDENT_DEUDORA) %>%
  distinct() %>%
  nrow()

uLinksN

```
# Build the Average Network
$W$ is the average for each link between 1997q4 and 2000q4 for all banks

```{r}
avgRelations <- thisRelations %>%
  group_by(IDENT_ACREEDORA, IDENT_DEUDORA) %>%
  summarise(WEIGHT = mean(WEIGHT)) %>%
  # W can only contains entities that are in the sample. 
  semi_join(., select(banks, IDENT), 
    by= c('IDENT_ACREEDORA' = 'IDENT')) %>%
  semi_join(., select(banks, IDENT), 
    by= c('IDENT_DEUDORA' = 'IDENT'))
# This dataframe should be empty
netExcBanks <- bind_rows(anti_join(avgRelations, banks, by=c('IDENT_ACREEDORA' = 'IDENT')),
                    anti_join(avgRelations, banks, by=c('IDENT_DEUDORA' = 'IDENT')))

avgRelations

writexl::write_xlsx(avgRelations, path=str_c(samPath, 'avgRelations.xlsx'))

```
The following entities appear in the network but not in the banks dataframe:
`{r} netExcBanks`. Should be empty!


## Export average network as spatial matrix
 Export the network as a fix spatial matrix `W` which only contains banks that are in `banks`
 
```{r }
nodes <- banks %>%
  filter(., fechaQ==1997.4) %>%
  select(., IDENT, NOMRED, exitDateQ:GRUPO_ID_UNI)
  
g <- igraph::graph_from_data_frame(d = avgRelations, 
                           vertices = nodes,
                          directed = TRUE)

# Export adjacency matrix
W_weighted <- as_adjacency_matrix(g, attr='WEIGHT', sparse=FALSE)
W <- as_adjacency_matrix(g, attr=NULL, sparse=FALSE)
# Dimensions of W should equal # of banks
```

There are `{r} nrow(thisRelations)` links in `thisRelations`; `{r} nrow(uLinksN)` of them are unique and hence the average network has `{r} nrow(W)` non-empty cells.

# Build covariates and dependant
I collect covariates X for each quarter of banks alive. We only consider banks existing at 1997q4. This allows having a fix W, otherwise W changes every quarter. Aditionally, excludes new born banks wich are more likley to fail. 

Build individual samples
```{r}

Qs = c(1997.4, 1998.1, 1998.2, 1998.3, 1998.4, 1999.1, 1999.2, 1999.3, 1999.4,
       2000.1, 2000.2, 2000.3, 2000.4, 2001.1, 2001.2, 2001.3, 2001.4)
samT <- map(Qs, function(thisQ) {
  #thisQ = 1998.4
  sam_t <-  banks %>%
    # Only observations at this time
    filter(fechaQ == thisQ)
  
  #Bank covariates (X)
  varsList <- c('IDENT', 'ActivoN', 'C8Est_w', 'CAR_IRR_3A6', 'P_ROA', 'P_DEP_ARS_RATE',
                'P_LOANS_ARS_RATE_W', 'APRSpNF_RATE_W', 'APR_USD_RATE', 'APR_RATE_W')
  X_t <- sam_t %>%
    select(all_of(varsList))
  
  # Vector y
    # 1: survival, 0: failure during the sample period
  y_t <- if_else(sam_t$exitDateQ <= thisQ, 0, 1)
  
  avgPastRelations <- thisRelations %>%
    filter(fechaQ <= thisQ) %>%
    group_by(IDENT_ACREEDORA, IDENT_DEUDORA) %>%
    summarise(avgW = mean(WEIGHT)) %>%
    # W can only contains entities that are in the sample. 
    semi_join(., select(sam_t, IDENT), 
      by= c('IDENT_ACREEDORA' = 'IDENT')) %>%
    semi_join(., select(sam_t, IDENT), 
      by= c('IDENT_DEUDORA' = 'IDENT'))
  
  list('y'=y_t, 'X'=X_t, 'avgLinks_t'=avgPastRelations)
  
})

names(samT) <- Qs

saveRDS(samT, 'samT.rds')
```

# Export to Matlab

map(samT, function(tt) {
  
  nodes <- select(sam, IDENT, NOMRED, EXIT_DATE_Q:GRUPO_ID_UNI)
g <- graph_from_data_frame(d = theseRelations, 
                           vertices = nodes,
                          directed = TRUE)

# Export adjacency matrix
W_weighted <- as_adjacency_matrix(g, attr='WEIGHT', sparse=FALSE)
W <- as_adjacency_matrix(g, attr=NULL, sparse=FALSE)
 
  list('y' = as.vector(tt$y),
       'X' = data.matrix(tt$X),
       'W' = 
})
library(rmatio)

exp <- list('1997.4' = list('X' = cbind(c(1,2,3), c(4,5,6)),
                'y' = c(1, 1, 1, 2)),
            '1998.1' = list('X' = cbind(c(1,2,3), c(4,5,6)),
                'y' = c(1, 1, 1, 2)))

write.mat(exp, 'matExp.mat')
write.mat(samT$`1997.4`, 'matExp.mat')
exp$a$`y`
```

```{r build_networ}
# Look for apropiate network
networkT <- map(Qs, function(thisQ) {
  thisQ = 1998.4
  # Option A: chose avg past links
  

  avgPastRelations
  theseRelations <- 
  
  theseRelations <- semi_join(avgRelations, select(sam, IDENT), 
                              by= c('IDENT_ACREEDORA' = 'IDENT')) %>%
                    semi_join(., select(sam, IDENT), 
                            by= c('IDENT_DEUDORA' = 'IDENT'))
  
```

names(samT) <- Qs

filter_all() %>%
          
filter(banks, FECHA_M = atDate

```