---
title: "My first Spatial Matrix"
author: "Emi"
date: "06/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(igraph)
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs

```

## R Markdown
 Now I build a graph from the bilateral relationships between entities.
 First, make sure no bilateral connections with the same bank:

```{r graph}
actors <- data.frame(name=c("Alice", "Bob", "Cecil", "David",
                            "Esmeralda"),
                     age=c(48,33,45,34,21),
                     gender=c("F","M","F","M","F"))
relations <- data.frame(from=c("Bob", "Cecil", "Cecil", "David",
                               "David", "Esmeralda"),
                        to=c("Alice", "Bob", "Alice", "Alice", "Bob", "Alice"),
                        same.dept=c(FALSE,FALSE,TRUE,FALSE,FALSE,TRUE),
                        friendship=c(4,5,5,2,1,1), advice=c(4,5,5,4,2,3))
g <- graph_from_data_frame(relations, directed=TRUE, 
                           vertices=actors)
print(g, e=TRUE, v=TRUE)

```

Acces a specific node (vertix):

```{r}
V(g)[[1]]
```
gives all the details about the first vertix.

 
 We can plot g
```{r plot}
library(ggraph) 
ggraph(g, layout='fr', weights=friendship ) +
  geom_edge_link() +
  geom_node_point(aes(size = centrality_pagerank())) +
  theme(legend.position = 'bottom')

ggraph(g, layout='fr', weights=friendship ) +
  geom_edge_link() +
  geom_node_point(aes(size = age), colour='blue', alpha=.2) +
  geom_node_text(aes(label = name), repel=TRUE) + 
  theme(legend.position = 'bottom')

```
 
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
