---
title: "Graph 1997m6-2001m12"
author: "Emi"
date: "10/02/2021"
output: html_document
---

```{r setup, include=FALSE}
getwd()
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(xlsx)
library(svglite) # export plots to svg
#source('FunsMisc.R')
```

## Loading data

Load the database from Stata:

```{r load_and_filter}
dbRelations <- read_dta('../../data/interLoans/cen_deu_1997-06_2001-06_todas_ent_fcieras.dta') %>%
              dplyr::select(., FECHAdata, IDENT_ACREEDORA, IDENT_DEUDORA, PRESTAMOS) %>%
              dplyr::filter(., !is.na(IDENT_DEUDORA)) %>%
              dplyr::mutate(., FECHAdata = ymd("1960-01-01")+months(FECHAdata))
dbFcialEnts <- read_dta('../../data/DBbanks/capital-allEntities-Monthly.dta', col_select = c(IDent, FECHAdata, bNombre, grupoIDUni, Activo, ActivoR,
                      ALIQs1_1ratio, APRamplio, C8Est_w, CAR_IRR_3A6,
                      P_LOANS_ARS_RATE, P_DEP_ARS_RATE, P_ROA, C8_E)) %>%
                dplyr::mutate(., FECHAdata = ymd("1960-01-01")+months(FECHAdata),                        IDENT_ACREEDORA = IDent) %>%
                filter(., FECHAdata<ymd("2004-12-01") & FECHAdata>ymd("1997-05-01"))
```

### Weighting relations

Now we build the wights of each link. We backup the data on Assets and Loans from dbFcialEnts and enter into the dbRelations data frame.

```{r build_graph}
relations <- dbRelations %>%
              filter(., IDENT_ACREEDORA != IDENT_DEUDORA) %>%
              dplyr::left_join(., dbFcialEnts, by = c('IDENT_ACREEDORA', 'FECHAdata'))

```

## Oh missing values!

### From creditors perspective

The following entities appear in the Central de deudores but not anymore in the balance de saldos:

```{r}
missCreditors <- dplyr::anti_join(relations, dbFcialEnts, 
                                  by=c('FECHAdata', 'IDENT_ACREEDORA'))
missCreditors

```

The **318 Banco de Salta SA** which was absorbed by Banco Macro on November 1999. I have detailed data only till Sep-1999. I could get more aggregated data if necesary from the balance resumido. **Caja de crédito Universo Cooperativa Limitada 64123** did not report its balance in 2000-10. I treat it as a missing value.

I impute this missing values. Replace with the previous value

```{r }
toAddSalta <- filter(dbFcialEnts, FECHAdata == ym(199909) &IDent == 318) %>%
            mutate(., FECHAdata = ym(199910))
toAddUniverso <- filter(dbFcialEnts, FECHAdata == ym(200009) &IDent == 64123) %>%
                  mutate(., FECHAdata = ym(200010))
dbFcialEnts <- bind_rows(dbFcialEnts, toAddSalta, toAddUniverso) 
```

### From debtors perspective

Verify that all nodes involved in relations are in dbFcialEnts. The following table shows the relations in which a debtor does not appear in dbFcialEnts. *anti\_join()*, returns rows in *relations* without a match in *dbFcialEnts*.

```{r}
missDebtors <- anti_join(relations, 
                    mutate(dbFcialEnts, IDENT_DEUDORA = IDent),
                    by=c('FECHAdata', 'IDENT_DEUDORA')) %>%
                  group_by(., IDENT_DEUDORA) %>%
                  summarise(n = n())
missDebtors
```

This could be due to debtors disappearing. A debtor disappears as a financial entitite but the debts do not expire, such that active financial entities still report those debts.

I exclude these relations from the *relations* tibble. We exclude those observations and select a specific month, say, **1999m12**

Get desc stats monthly?

```{r network_by_date}
#relations <- filter(relations, !is.na(IDent))
atDate <- ymd("1998-06-01")
theseRelations <-  relations[ !(relations$IDENT_DEUDORA %in% missDebtors$IDENT_DEUDORA),  ] %>%
                  dplyr::mutate(., WEIGHT = PRESTAMOS/APRamplio) %>%
                  dplyr::filter(., WEIGHT>0.005)

grupoStr <- tibble('grupoIDUni' = c(1:9, NA),
                    'type' = c('Local corporation', 'Cooperative', 'Local corporation', 'State-owned', 'State-owned', 'Foreign branch', 'Caja', 'Non-bank', 'Non-bank', 'Non-bank'))

nodes <- filter(dbFcialEnts, FECHAdata==atDate) %>%
          dplyr::select(., !FECHAdata) %>%
          left_join(., grupoStr, by='grupoIDUni')
```

When did these bank end in 'entidades.dta'?

```{r, eval=FALSE}
dbEnts <- read_dta('../BasesBCRA-IEF/entidades/entidades.dta') %>%
          dplyr::mutate(., FECHAdata = ymd("1960-01-01")+months(FECHAdata))
entsDates <- dbEnts %>%
              group_by(., IDent) %>%
              summarise(firstDate = min(FECHAdata), endDate = max(FECHAdata))
#save2Excel(entsDates, 'entsDates',  'entsDates.xlsx')
entsDates
```

## Relations: distribution of weights

```{r weight_density}
#thisRelations <- dplyr::filter(theseRelations, FECHAdata == atDate)
group_by(theseRelations, FECHAdata) %>%
  summarise(.,
          'Links' = n(),
          'N_CREDITORS' = n_distinct(IDENT_ACREEDORA),
          'N_DEBTORS' = n_distinct(IDENT_DEUDORA),
          'MEAN_WEIGHT_PC' = round(mean(WEIGHT)*100, 2),
          'Median' = round(median(WEIGHT)*100),
          'CV' =  round((MEAN_WEIGHT_PC/100) / sd(WEIGHT), 2),
          '1st quartile_PC' = round(quantile(WEIGHT, probs=.25)*100, 2))

```

ggplot(data=thisRelations[, 'WEIGHT'], mapping=aes(x=WEIGHT)) +
  scale_x_continuous(breaks=seq(0, 0.35, by=0.05)) +
  geom_dotplot()

ggplot(data=thisRelations[, 'WEIGHT'], mapping=aes(x=WEIGHT)) +
  scale_x_continuous(breaks=seq(0, 0.35, by=0.05)) +
  geom_boxplot()

```

# Build the network

```{r }
g <- graph_from_data_frame(
  thisRelations %>% dplyr::select(., IDENT_ACREEDORA, IDENT_DEUDORA, WEIGHT), 
    vertices = nodes,
    directed = TRUE)
```

Acces a specific node (vertix):

```{r}
V(g)[[1]]
```

gives all the details about the first vertix.

We can plot g

```{r plot}
library(ggraph) 
ggraph(g, layout='fr', weights=WEIGHT ) +
  geom_edge_link() +
  geom_node_point(aes(size = centrality_pagerank())) +
  theme(legend.position = 'bottom')

Pstatic <- ggraph(g, layout='fr', weights=WEIGHT ) +
            # geom_edge_fan(aes(width=WEIGHT, colour=stat(index)),
            geom_edge_fan(aes(alpha=WEIGHT),
                          arrow = arrow(length=unit(1, 'mm')), end_cap = circle(2, 'mm')) +
            geom_node_point(aes(size = (Activo/1000000), colour=factor(type)), alpha=.8) +
            #geom_node_text(aes(label = bNombre), repel=TRUE, check_overlap = TRUE) + 
  scale_size(breaks=c(1, 5, 10, 15), labels=c('<=1', '5', '10', '15'))          +
  theme(legend.position = 'bottom') +
            guides(size=guide_legend(title='Assets (billions pesos)', title.position='top', nrow=3, ncol=2, byrow=TRUE),
                   colour=guide_legend(title='Organizational type', title.position='top', override.aes=list(size=5), nrow=3, byrow=TRUE),
                   edge_alpha=guide_legend(title='Share from lender bank', title.position='top', nrow=3, byrow=TRUE))

Pstatic
ggsave('Pstatic.pdf', plot=Pstatic)
ggsave('Pstatic.svg', plot=Pstatic)

```

## Interactive plot

Using visNetwork package. I use the same 'g' object from iGraph

```{r plot_interactive, eval=TRUE}
pTblNodes <- nodes %>%
  dplyr::select(., IDent, bNombre, Activo) %>%
  dplyr::transmute(., id=IDent, label=bNombre, value=Activo, title=str_c(bNombre, ', $ ', (Activo/10000), ' mill.'))

pTblRelations <- thisRelations %>%
  dplyr::transmute(., from=IDENT_ACREEDORA, to=IDENT_DEUDORA, value=WEIGHT, arrows='to')

visNetwork(nodes = pTblNodes, edges = pTblRelations)  %>% 
  visLayout(randomSeed = 123, improvedLayout=TRUE) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visInteraction(navigationButtons = TRUE) %>%
  visConfigure(enabled = TRUE)
#%>%
#  visNodes(scaling=list())



#visIgraph(g) %>%
#  visNodes(shape='square', size = WEIGHT)
```

# Export adjacency matrix

```{r adj_matrix}
W <- as_adjacency_matrix(g, attr='WEIGHT', sparse=FALSE)
```
