---
title: "Tables"
format: html
params:
  PSAR_COVAR: TRUE # if TRUE std error for SAR Probit is computed from the var-cov matrix instead of the precision one
---


```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(readODS)
library(spdep)
library(spatialreg)
library(huxtable) # export tables (tibble) to Latex/Excel
library(Matrix)
library(ProbitSpatial)
library(texreg)
source('../../Rutils/Emi_R_utils.R')
source('../../Rutils/texreg_extension_ProbitSpatial.R')
source('../../Rutils/texreg_extension_sphet.R')
source('../../BAFA_funs.R')

```


# BOOT 

## Specs

```{r}
# For output tables SPATIAL MODELS
coefNamesMap <- list("(Intercept)" = 'Intercept',
                    'log(ActivoN)' = 'ln(Assets)',
                     'CAR_IRR_3A6' = 'Non-performing loans',
                     'P_LOANS_ARS_RATE_W' = 'Loans interest rate',
                     'APRSpNF_RATE_W' = 'Govt. loans to Loans',
                     'APR_USD_RATE' = 'USD loans to Loans',
                     'APR_RATE_W' = 'Loans-to-Assets ratio',
                     'C8Est_w' = 'Equity-to-Assets ratio',
                     'P_ROA' = 'ROA',
                     'P_DEP_ARS_RATE' = 'Deposits interest rate',
                     'rho' = 'rho',
                    'lambda' = 'rho')
tabSpecs <- list('custom.coef.map' = coefNamesMap,
                 'stars' = c(0.01, 0.05, 0.10, 0.15),
                  'siunit' = TRUE,
                 'digits' = 2,
                 'booktabs' = TRUE,
                 'groups' = list("\\textbf{Size}" = 1:2,
                               "\\textbf{Asset-side risk}" = 3:7,
                               "\\textbf{Funding}" = 8:10,
                               "\\textbf{Spatial}" = 11),
                 'useCovar' = params$PSAR_COVAR) # how std error for probtiSAR should be computed? 

# For output tables NON-SPATIAL MODELS (Probit)
coefNamesNonSp <- c(NA, 'ln(Assets)', 
      'Non-performing loans', 'Loans interest rate', 'Govt. loans to Loans', 'USD loans to Loans', 'Loans-to-Assets ratio',
       'Equity-asset ratio', 'ROA', 'Deposits interest rate')
tabSpecsNonSp <- list('custom.coef.names' = coefNamesNonSp,
                 'stars' = c(0.05, 0.10, 0.15),
                  'siunit' = TRUE,
                 'digits' = 2,
                 'booktabs' = TRUE,
                 'groups' = list("Size" = 1:2,
                               "Asset-side risk" = 3:7,
                               "Funding" = 8:10))

```
## Load data

```{r}
R <- readRDS('../_model.rds')
```

# BASELINE RESULTS

Failure till 2001q3: LPM, SAR LPM, Probit, SAR Probit
Probit, SAR Probit . Before and after 2001

### Baseline: 4-model estimates


```{r}
thisSam <- 'A98_W98_B2L_nz_99FT01q3'
tM <- list(R$probit[[thisSam]],
          R$SARProbit[[thisSam]],
          R$LPM[[thisSam]],
          R$SARHet[[thisSam]])
          
          #extract_sphet_effects(R$SARHet$A98_W98_B2L_nz_99FT01q3$effects_direct))

modNamesLong <- c('Probit',
                  'SAR Probit',
                  'LPM',
                  'SAR LPM')
do.call(texreg, c('l'= list(tM),
                  'caption'= list("Spatial and non-spatial model. Baseline. "),
                  'custom.model.names' = list(modNamesLong),
                  tabSpecs)) %>%
  gsub("^{*", "*", ., fixed=TRUE) %>%
  gsub("*}", "*   ", ., fixed=TRUE) %>%
  gsub("^{\\cdot} ", "\\str{\\cdot}", ., fixed=TRUE) %>%
  gsub("} & {", "}\n & {", ., fixed=TRUE)

```

### Baseline: marginal effects

```{r}
samName <- 'A98_W98_B2L_nz_99FT01q3'
# coeficient names must be the same acorss models

texRegs <- list('Probit'=NULL, 
                'SARProbitDirect'=NULL, 'SARProbitIndirect'=NULL, 'SARProbitTotal'=NULL,
                'LPM'=NULL, 
                'SARLPMDirect'=NULL, 'SARLPMIndirect'=NULL, 'SARLPMTotal'=NULL)
  
# Probit
texRegs$Probit <-   createTexreg(
    coef.names = rownames(R$probitEffects[[samName]]),
    coef = R$probitEffects[[samName]][, 1],
    se = R$probitEffects[[samName]][, 2],
    pvalues = R$probitEffects[[samName]][, 4]  )

# SAR probit
texRegs$SARProbitDirect <- createTexreg(coef.names = R$SARprobitMgEff[[samName]]$predictor,
                                        coef = R$SARprobitMgEff[[samName]]$direct)
texRegs$SARProbitIndirect <- createTexreg(coef.names = R$SARprobitMgEff[[samName]]$predictor,
                                        coef = R$SARprobitMgEff[[samName]]$indirect)
texRegs$SARProbitTotal <- createTexreg(coef.names = R$SARprobitMgEff[[samName]]$predictor,
                                        coef = R$SARprobitMgEff[[samName]]$total)
# LPM
texRegs$LPM <- R$LPM[[samName]]
# SAR LPM
texRegs$SARLPMDirect <- extract_sphet_effects(R$SARHetEffects[[samName]]$direct)
texRegs$SARLPMIndirect <- extract_sphet_effects(R$SARHetEffects[[samName]]$indirect)
texRegs$SARLPMTotal <- extract_sphet_effects(R$SARHetEffects[[samName]]$total)


modNamesLong <- c('Probit',
                  'SAR Probit direct',
                  'SAR Probit indirect',
                  'SAR Probit total',
                  'LPM',
                  'SAR LPM direct',
                  'SAR LPM indirect',
                  'SAR LPM total')

do.call(texreg, c('l'= list(texRegs),
                  'caption'= list("Spatial and non-spatial model. Baseline. "),
                  'custom.model.names' = list(modNamesLong),
                  'omit.coef' = '(Intercept)',
                  list('custom.coef.map' = coefNamesMap[-(1)],
                 'stars' = c(0.01, 0.05, 0.10, 0.15),
                  'siunit' = TRUE,
                 'digits' = 2,
                 'booktabs' = TRUE,
                 'groups' = list("\\textbf{Size}" = 1,
                               "\\textbf{Asset-side risk}" = 2:6,
                               "\\textbf{Funding}" = 7:9),
                 'useCovar' = params$PSAR_COVAR) # how std error for probtiSAR should be computed?
                 )) %>%
  gsub("^{*", "*", ., fixed=TRUE) %>%
  gsub("*}", "*   ", ., fixed=TRUE) %>%
  gsub("^{\\cdot} ", "\\str{\\cdot}", ., fixed=TRUE) %>%
  gsub("} & {", "}\n & {", ., fixed=TRUE)

```

Use http://www.listdiff.com/align-csv-text-columns-online-tool to align on "&". Get rid of title row before alignment.


# ADITIONAL RESULTS

## Failures till 2003q4

Replicate the main table with 4 models including failures till 2003q4

```{r}
thisSam <- 'A98_W98_B2L_nz_99FT03q4'
tM <- list(R$probit[[thisSam]],
          R$SARProbit[[thisSam]],
          R$LPM[[thisSam]],
          R$SARHet[[thisSam]])
          
          #extract_sphet_effects(R$SARHet$A98_W98_B2L_nz_99FT01q3$effects_direct))

modNamesLong <- c('Probit',
                  'SAR Probit',
                  'LPM',
                  'SAR LPM')
do.call(texreg, c('l'= list(tM),
                  'caption'= list("Spatial and non-spatial model. Baseline. "),
                  'custom.model.names' = list(modNamesLong),
                  tabSpecs)) %>%
  gsub("^{*", "*", ., fixed=TRUE) %>%
  gsub("*}", "*   ", ., fixed=TRUE) %>%
  gsub("^{\\cdot} ", "\\str{\\cdot}", ., fixed=TRUE) %>%
  gsub("} & {", "}\n & {", ., fixed=TRUE)


```

## Different networks

All SAR probit, 6 diferent networks: 3 directed but unweighted (U), 3 undrected and thus unweighted (UU)

%& {Probit SAR A98_W98unw_B2L_nz_99FT01q3}
 %& {Probit SAR A98_W97_B2L_nz_99FT01q3}
 %& {Probit SAR A98_W99t01q3NoRest_B2L_nz_99FT01}
 %& {Linear SAR A98_W98_B2L_nz_99FT01q3} 

```{r}
# Baseline is A98_W98_B2L_nz_99FT01q3

tM <- list(R$SARProbit[['A98_W98_B2L_nz_99FT01q3']],
          R$SARProbit[['A98_W98unw_B2L_nz_99FT01q3']],
          R$SARProbit[['A98_W97_B2L_nz_99FT01q3']],
          #R$SARProbit[['A98_W97rest_B2L_nz_99FT01q3']],
          R$SARProbit[['A98_W99t01q3NoRest_B2L_nz_99FT01']],
          R$SARProbit[['A98_W98und_B2L_nz_99FT01q3']],
          R$SARProbit[['A98_W97und_B2L_nz_99FT01q3']],
          R$SARProbit[['A98_W99t01q3und_B2L_nz_99FT01q3']])
modNamesLong <- c('Baseline $\bar{W}_{98}$',
                  '$\bar{W}_{98, U}$',
                  '$\bar{W}_{97}$',
                  '$\bar{W}_{99-01}$',
                  '$\bar{W}_{98, UU}$',
                  '$\bar{W}_{97, UU}$',
                  '$\bar{W}_{99-01, UU}$')

do.call(texreg, c('l'= list(tM),
                  'caption'= list("Additional results"),
                  'custom.model.names' = list(modNamesLong),
                  tabSpecs)) %>%
  gsub("^{*", "*", ., fixed=TRUE) %>%
  gsub("*}", "*   ", ., fixed=TRUE) %>%
  gsub("^{\\cdot} ", "\\str{\\cdot}", ., fixed=TRUE) %>%
  gsub("} & {", "}\n & {", ., fixed=TRUE)

#R$SARHet[['A98_W98_B2L_nz_99FT03q4']]
# 'Linear SAR A98_W98_B2L_nz_99FT03q4'

```
