---
title: "Annual98_pastAvgW_creW"
author: "Emi"
date: "01/09/2021"
output: html_document
code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
library(tidyverse)
library(lubridate)
library(tsibble) # Panel data/longitudinal
library(haven) # Access to Stata databases
library(tidygraph) # Plotting graphs
library("igraph", quietly = TRUE, warn.conflicts = FALSE, verbose = FALSE)
require(visNetwork)
library(writexl)
library(svglite) # export plots to svg
library(rmatio) # expor to Matlab
library(spdep)
library(spatialreg)
source('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/code/Rutils/Emi_R_utils.R')

```

```{=html}
<style type="text/css">
.main-container {
  max-width: 1000px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

```{r sample_specs}
specs <- list(
  'samFile' = 'sam_s98.Priv.01.onT.rds',
  'y' = list('failureSince' = 2000.1,
             'failureHorizon' = 2001.4),
  'X' = list('bankBirthFrom' = 1997.4, 
             'vars' = c('ActivoN', 'C8Est_w', 'CAR_IRR_3A6', 'P_ROA', 'P_DEP_ARS_RATE',
                        'P_LOANS_ARS_RATE_W', 'APRSpNF_RATE_W', 'APR_USD_RATE', 'APR_RATE_W')),
  'W' = list('from' = '',
             'to' = '1997q4',
             #Weights from debtor/creditor perspective : W_D_PR/W_A_PR (Deudora / Acreeedora)
             'wVar' = 'W_A_PR'))
```
# INtroduction

-   $\bm{y_t}$ is 1 if the bank fails between `r specs$y$failureSince` and `r specs$y$failureHorizon`.

-   $W$ is the average between 1997q4 and `r specs$W$to`. Hence we use past information about the network.

-   $X$ is the average for 1998.

# Load data

```{r load_bank_data}
#setwd('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
banksDB <- haven::read_dta('data/failures-1997-2001-annual.dta') %>%
  dplyr::mutate(., 
        fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
        exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
        startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
        .after = IDENT) 
  
banks <- banksDB %>%
  drop_na %>%
  filter(FECHA_A == 1998) %>%
  # ONly private banks
  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5) %>%
  filter(startDateQ<= !!specs$X$bankBirthFrom & exitDateQ >= !!specs$y$failureSince) 
```

```{r}
setwd('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
#banksDB <- haven::read_dta('data/BAFA-main-1997-2001-quarterly.dta') %>%
#        dplyr::mutate(., 
#        fechaQ = quarter(as_date(FECHA_D, origin=ymd('1960-01-01')), with_year=TRUE),
#        exitDateQ = quarter(as_date(EXIT_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
#        startDateQ = quarter(as_date(FIRST_DATE, origin=ymd('1960-01-01')), with_year=TRUE),
#        .after = IDENT) %>%
#    drop_na %>%
#  # For fix W I need to fix banks at the beginning of the sample
#  filter(startDateQ<= 1997.4 & exitDateQ>=2000.1) %>%
#  # ONly private banks
#  filter(GRUPO_ID_UNI != 4 & GRUPO_ID_UNI !=5)

# Select only entities private and alive on 1997q4
banksAtStart <- banksDB %>%
dplyr::group_by(IDENT) %>%
  summarise('start' = FECHA_A,
            'startDateQ' = min(startDateQ),
            NOMRED = first(NOMRED),
            GRUPO_ID_UNI = first(GRUPO_ID_UNI),
            P_LOANS_ARS_RATE_W = first(P_LOANS_ARS_RATE_W))

excBanks <- filter(banksDB, startDateQ>1997.4)
```

I lose `r NROW(excBanks)` banks because a) they don't have complete observations by 1997.4 (missing P_LOANS_ARS_RATE) or b) they were privatised after 1997q4.

```{r}
excBanks
```

Hence I end up with `r banks$IDENT %>% unique() %>% NROW()` banks.

```{r load_network_data}
setwd('C:/Users/emi.ABLE-22868/OneDrive/UWA PhD/bankFailure/')
dbRelations <- read_dta('data/interLoans/cen_deu_1997-06_2001_quarterly.dta') %>%
  mutate(FECHA_Q = ( as_date(FECHA_D, origin=ymd("1960-01-01")) %>% 
                     tsibble::yearquarter(.) ),
         WEIGHT = .data[[ specs$W$wVar]]*100) %>%
  tsibble(key = c(IDENT_ACREEDORA, IDENT_DEUDORA), 
          index = FECHA_Q)

# W_A_PR W_D_PR
thisRelations <- filter_index(dbRelations, ~ specs$W$to) %>%
  # fechaQ >= 1997.4 &
  filter(., (IDENT_ACREEDORA != IDENT_DEUDORA) &
  WEIGHT != 0)

thisRelations

# Number of unique relations (links)
uLinksN <- select(thisRelations, IDENT_ACREEDORA, IDENT_DEUDORA) %>%
  distinct() %>%
  nrow()

uLinksN

```


# Estimation of a linear ols model

## Build objects

```{r}
X <- banks %>% select(all_of(specs$X$vars))

# 1: survival, 0: failure during the sample period
  y <- if_else(banks$exitDateQ <= specs$y$failureHorizon, 0, 1)
  
```

```{r save, eval=FALSE}
write.mat(list('Wstd' = Wstd,
               'X' =  X %>% data.matrix(.),
               'y' = y),
          'data.mat')
```

## Desc stats

```{r descStatsBanks}
bind_cols('y'=y, X, 'IDENT'=banks$IDENT) %>% 
  descStats2(.)
```

There are `r NROW(X)` observations and `r banks$IDENT %>% unique() %>% NROW()` 

```{r estimation_ols}
reg <- lm(formula ='y ~ ActivoN + C8Est_w + CAR_IRR_3A6+ P_ROA+ P_DEP_ARS_RATE +
        P_LOANS_ARS_RATE_W+ APRSpNF_RATE_W+ APR_USD_RATE+ APR_RATE_W',
        data = bind_cols('y'=y, X))

summary(reg)
```

